A Method for Regularisation of Evolutionary Polynomial Regressions using Support Vector Machines

### 2013-11-21 texts/submission_02-asc/paper_spfga-review.tex
start working on motivation

The empiric conclusion of those experiments is that \ac{EPRR} achieves better errors than the other non-ensemble methods and shorter computation time than plain \ac{EPR}.
\end{abstract}
%
\begin{keyword}
evolutionary polynomial regression \sep regularisation \sep feature extraction \sep dimensionality reduction 
\end{keyword}
\end{frontmatter}
%
%	Line numbers for revision
%
%
%\linenumbers
%
\section{Introduction}

With notable exceptions (\emph{e.g.} neural networks) machine learning regression techniques produce linear models. The linearity assumption has many advantages including reduced computational complexity and strong the\-o\-re\-ti\-cal framework. However nonlinearity is unavoidable in many application scenarios, specially those with phase transitions or feedback loops, so common in engineering, ecology, cybernetics and other areas. The kernel trick in \acp{SVM} (\cite{scholkopf1997kernel,liang2012eigen,Bao:2013aa}) alleviates this problem by allowing special non-linear transformations of the feature-space. The condition such transformations must meet is known as the \emph{kernel trick}, $k\at{x,x'} = \left< \varphi\at{x}, \varphi\at{x'} \right>$, where $\varphi$ is the feature-space transformation and $\left<\cdot,\cdot\right>$ denotes inner product. The ``trick'' consists on computing the kernel $k\at{x,x'}$ while avoiding the computation of the inner product and the transformations $\varphi\at{x}, \varphi\at{x'}$. A special case of polynomial transformation, the \emph{polynomial kernel}, $k\at{x,x'} = \left<x,x'\right>^d$ is commonly used in regression and classification tasks with \acp{SVM}. However general polynomial transformations do not verify the kernel trick.

>>>>

The empiric conclusion of those experiments is that \ac{EPRR} achieves better fitting than the other non-ensemble methods and shorter computation time than plain \ac{EPR}.
\end{abstract}
%
\begin{keyword}
evolutionary polynomial regression \sep regularisation \sep feature extraction \sep dimensionality reduction 
\end{keyword}
\end{frontmatter}
%
%	Line numbers for revision
%
%
%\linenumbers
%
\section{Introduction}

With notable exceptions (\emph{e.g.} neural networks) machine learning regression techniques produce linear models. The linearity assumption has many advantages including reduced computational complexity and strong the\-o\-re\-ti\-cal framework. However nonlinearity is unavoidable in many application scenarios, specially those with phase transitions or feedback loops, so common in engineering, ecology, cybernetics and other areas. The kernel trick in \acp{SVM} (\cite{scholkopf1997kernel, liang2012eigen, Bao:2013aa}) alleviates this problem by allowing special non-linear transformations of the feature-space. The condition such transformations must meet is known as the \emph{kernel trick}, $k\at{x,x'} = \left< \varphi\at{x}, \varphi\at{x'} \right>$, where $\varphi$ is the feature-space transformation and $\left<\cdot,\cdot\right>$ denotes inner product. The ``trick'' consists on computing the kernel $k\at{x,x'}$ while avoiding the computation of the inner product and the transformations $\varphi\at{x}, \varphi\at{x'}$. A special case of polynomial transformation, the \emph{polynomial kernel}, $k\at{x,x'} = \left<x,x'\right>^d$ is commonly used in regression and classification tasks with \acp{SVM}. However general polynomial transformations do not verify the kernel trick.
